The pollination trade-off

### 2018-12-01 paper/manuscript.Rmd
Change plant strategies subheading to flexibility of plant strategies
Add paragraph effect of each variable results

## Plant strategies

@@

```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination. Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.). Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets."}
height1 <- 1
height2 <- 1.29
# pdf(width = 3.25 * 2, height = sum(c(height1, height2)))
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 6.5/5*2
mult <- 2.355 # for 2/3 is 2.125, for 3/5 is 2.355
width_coef_1 <- (6.5 - width_imp) / (1 + mult)
width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
drake::loadd(fig_coefficient_averages)

>>>>

## Flexibility of plant strategies

@@

Out of the four variables we explored, we found that the plants' mean visit efficacy and its abundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a). 
Surprisingly, the number of shared pollinators was comparatively unimportant as it was only included in models with relatively large AICc values. 
We found that the sign of the relationship between our ecological factors and pollen deposition tended to be the same for both conspecific and heterospecific pollen. 
This is, factors that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
The plants' mean visit efficacy had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
The positive association with conspecific pollen indicates a positive effect of visit efficacy on the quantity of pollination. 
However, the difference between the coefficient that relates visit effectiveness to heterospecific and conspecific pollen deposition suggests a marginal negative relationship of this variable and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c). 
Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination. 
Functional originality had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
And, finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to all other ecological factors. 
Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).

```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of ecological factors in the pollination service**. (a) The plant's visit efficacy and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen. Meanwhile, the number of shared pollinators was relatively unimportant. The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable (b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen. Visit efficacy and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association. The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific (top panel) and heterospecific pollen (bottom panel). Results are only shown for models that included explanatory variable. (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and quality of pollination. The plot shows the mean effect (± SE) of the four analysed ecological variables in the quantity and quality of pollination."}
height1 <- 1
height2 <- 1.29
# pdf(width = 3.25 * 2, height = sum(c(height1, height2)))
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 6.5/5*2
mult <- 2.355 # for 2/3 is 2.125, for 3/5 is 2.355
width_coef_1 <- (6.5 - width_imp) / (1 + mult)
width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
drake::loadd(fig_coefficient_averages)
